---
title: "01/09/2024"
author: "Qianyi Xia"
date: "2024-01-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Note on T and F
Better to use TRUE and FALSE instead of T or F.

```{r demo in class, echo=TRUE, eval=TRUE}
x <- 1:10 * 10
y <- seq(10,100, by = 10)

x == y
```

```{r demo in class, echo=TRUE, eval=TRUE}
 x <- 1:5 # x is a vector of 1, 2, 3, 4, 5
 y<-x*3

 y %% 2 == 0 # the %% operator can be read "remainder after division by ..."
 # in this case, `y %% 2 == 0` will be TRUE if y is even

 areEven<-y%%2==0
 areEven
 # => c(FALSE, TRUE, FALSE, TRUE, FALSE)

 y[areEven]
 # => c(6, 12) 
 
 which(areEven)
 # return the sequence
```
## Paste0
paste0 is a sister function to paste which takes sep as an argument for what should be inserted between the strings given, and defaults to a single space.

```{r demo in class, echo=TRUE, eval=TRUE}
x <- "hello "
y <- "world"
z <- "!"
paste0(x, y, z)
#> "hello world!"

```
## Paste0
Use for loop to read csv files for each states in US
```{r demo in class, echo=TRUE, eval=TRUE}
state_data <- list() # start with an empty list

for (state in state.name) {  # state.name is a list of state names built into R

  # we'll talk more about reading in data later today
  new_data <- read.csv(file = paste0(state, ".csv")) 
  
  # create a list element for the data being read in named after the state
  state_data[[state]] <- state_data 
}

# clean up the state_data list
```

```{r demo in class, echo=TRUE, eval=TRUE}
for (i in 1:50) {
  print(paste0("the abbreviation for ", state.name[i], " is ", state.abb[i]))
}
```
## While
here’s a hypothetical: if you draw numbers between 1 through 10 randomly and sum them up, how long will it take you to get a value of at least 100?
```{r demo in class, echo=TRUE, eval=TRUE}
n_iterations <- 0 
value <- 0 
while (value < 100) {
  n_iterations <- n_iterations + 1
  value <- value + sample.int(n = 10, size = 1)
}
print(n_iterations)

```
what if we want to create a larger sample of data to see if our hypothesis was close to some observed data?
```{r demo in class, echo=TRUE, eval=TRUE}
iterations_needed <- numeric() # create an empty numeric vector

# we'll run the experiment 10,000 times so we have a substantial amount of data
for (i in 1:10000) {
  n_iterations <- 0 
  value <- 0 
  while (value < 100) {
    n_iterations <- n_iterations + 1
    value <- value + sample.int(n = 10, size = 1)
  }
  iterations_needed <- c(iterations_needed, n_iterations)
}

summary(iterations_needed)
```

##Use the here package

##Use Renv helps avoid version difference of code
makes your code more independent and valid and reproducable by other people.

#Other packages
target
rocker
```{r 1, echo=TRUE, eval=TRUE}


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
